---
title: "My Vignette For FARS"
author: "Raphael Monstein"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{My Vignette For FARS}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This package helps you to use Fatality Analysis Reporting System (FARS) data. It provides functions to load and analyze FARS data. The data is in a compressed format and can be found in the directory *inst/extdata*.

The package provides the following functions:
* fars_read
* make_filename
* fars_read_years
* fars_summarize_years
* fars_map_state

For details about each function, have a look at the documentation.

## Usage
*Note that you have to copy-paste the data into your working directory in order for the functions to work.*

To simply run the analysis and generate a plot, you can run the following:

```{r map_example}
library("myW4Assignment")
setwd("../inst/extdata")
fars_map_state(1, 2013)
```

If you are interested in a summary of the data, you could use the following code:

```{r summary_example}
library("myW4Assignment")
setwd("../inst/extdata")
fars_summarize_years(2013)
```
